```{r}
merged.tab.all <- read.csv("~/olwin_dowell_labs/reanalysis_07_28_20/merged_table_all_081020"  )
```

# make histograms
```{r}
merged.tab.all.numeric <- apply(as.matrix.noquote(merged.tab.all),2,as.numeric)
merged.tab.all.numeric <- merged.tab.all.numeric[,-1]

for (i in 1:length(colnames(merged.tab.all.numeric)))
{
  hist(log10(merged.tab.all.numeric[,i]), breaks = 100, ylim = c(0,1000), main = colnames(merged.tab.all.numeric)[i] )
}
```

### Boxplots with tidyr
```{r}
merged.tab.all.long <- gather(merged.tab.all, "condition", "measurement", -Var1)

library(ggplot2)

ggplot(merged.tab.all.long, aes(x=condition, y=measurement)) + geom_boxplot()
```

## Remove bias
```{r}
pruned.merged.tab.df1.bias <- merged.tab.all[which(merged.tab.all$DF1.R1.SR1 < 20),]
#pruned.merged.tab.df1.bias <- pruned.merged.tab.df1.bias[which(pruned.merged.tab.df1.bias$DF1.R2.SR3.TR1 < 20),]
#pruned.merged.tab.df1.bias <- pruned.merged.tab.df1.bias[which(pruned.merged.tab.df1.bias$DF1.R2.SR3.TR2 < 20),]
```

```{r}
unique.with.all.bias <- colSums(merged.tab.all[,2:36] != 0)
total.seq.with.all.bias <- colSums(as.matrix(merged.tab.all[,2:36]))


unique.without.df1.bias <- colSums(pruned.merged.tab.df1.bias[,2:36] != 0)
total.seq.without.df1.bias <- colSums(as.matrix(pruned.merged.tab.df1.bias[,2:36]))


meta.seq <- as.data.frame(cbind(unique.without.df1.bias,total.seq.without.df1.bias,unique.with.all.bias,total.seq.with.all.bias))

View(meta.seq)
```

```{r}
bias.barcodes <- list()
for (i in 1:nrow(pruned.merged.tab.df1.bias))
{
  if(length(as.vector(which(as.numeric(pruned.merged.tab.df1.bias[i,]) > 100))) > 3) 
    {bias.barcodes[[i]] <- i} 
}

bias.barcodesdf <- as.data.frame(unlist(bias.barcodes)) ## There are 90 barcodes that appear as >100 in more than 3 samples
  

for (i in 1:90)
{
  pruned.merged.tab.all <- pruned.merged.tab.df1.bias[-as.numeric(bias.barcodesdf$`unlist(bias.barcodes)`[i]),]
}

#For calculating percent bias
unique.without.all.bias <- colSums(pruned.merged.tab.all != 0)
total.seq.without.all.bias <- colSums(as.matrix(pruned.merged.tab.all[,2:36]))

write.csv(pruned.merged.tab.all, "~/olwin_dowell_labs/reanalysis_07_28_20/pruned_merged_table_all.csv", row.names = F)

```

```{r}
merged.tab.pruned.all.numeric <- apply(as.matrix.noquote(pruned.merged.tab.all),2,as.numeric)
merged.tab.pruned.all.numeric <- merged.tab.pruned.all.numeric[,-1]
```

```{r}
#row.names(merged.tab.pruned.all.numeric) <- row.names(pruned.merged.tab.all)
ll <- gather(pruned.merged.tab.all, "condition", "measurement", -Var1)

library(ggplot2)

ggplot(ll, aes(x=condition, y=measurement)) + geom_boxplot()
```

```{r}
for (i in 1:length(colnames(merged.tab.all.numeric)))
{
  onecolumn <- merged.tab.all.numeric[,i]
  onecolumn <- onecolumn[which(onecolumn != 0)]
  col.name <- colnames(merged.tab.all.numeric)[i]
  tmp1 <- list()
  tmp2 <- list()
      for (j in 1:length(onecolumn))
      {
        tmp1 <- rep(as.character(merged.tab.all$Var1[j]), onecolumn[j])
        tmp2 <- append(tmp2, tmp1) # this is not appending like we want
        print(head(tmp2))

        #tmp1 <- sample(tmp1$`rep.seq.vec$rep.seq`, 2400, replace = T)
      }
      #pruned.longform <- as.data.frame(unlist(tmp2))
      #colnames(pruned.longform) <- "repeatedseq" 

}
```

#### doing it the old fashioned slow way 
```{r}
#--------------------------DF1------------------------
tmp1 <- list()
tmp2 <- list()
for (i in 1:length(pruned.merged.tab.all$DF1.R1.SR1))
{
  tmp1 <- rep(as.character(pruned.merged.tab.all$seq[i]), pruned.merged.tab.all$DF1.R1.SR1[i])
  tmp2[[i]] <- tmp1
}
DF1.R1.SR1.pruned.longform <- as.data.frame(unlist(tmp2))
colnames(DF1.R1.SR1.pruned.longform) <- "repeatedseq" 

#--------------------------------------------------
tmp1 <- list()
tmp2 <- list()
for (i in 1:length(pruned.merged.tab.all$DF1.R2.SR3.TR1))
{
  tmp1 <- rep(as.character(pruned.merged.tab.all$seq[i]), pruned.merged.tab.all$DF1.R2.SR3.TR1[i])
  tmp2[[i]] <- tmp1
}
DF1.R2.SR3.TR1.pruned.longform <- as.data.frame(unlist(tmp2))
colnames(DF1.R2.SR3.TR1.pruned.longform) <- "repeatedseq" 

#--------------------------------------------------
tmp1 <- list()
tmp2 <- list()
for (i in 1:length(pruned.merged.tab.all$DF1.R2.SR3.TR2))
{
  tmp1 <- rep(as.character(pruned.merged.tab.all$seq[i]), pruned.merged.tab.all$DF1.R2.SR3.TR2[i])
  tmp2[[i]] <- tmp1
}
DF1.R2.SR3.TR2.pruned.longform <- as.data.frame(unlist(tmp2))
colnames(DF1.R2.SR3.TR2.pruned.longform) <- "repeatedseq" 

#--------------------------------------------------
tmp1 <- list()
tmp2 <- list()
for (i in 1:length(pruned.merged.tab.all$y.90.R1.SR1))
{
  tmp1 <- rep(as.character(pruned.merged.tab.all$seq[i]), pruned.merged.tab.all$y.90.R1.SR1[i])
  tmp2[[i]] <- tmp1
}
y.90.R1.SR1.pruned.longform <- as.data.frame(unlist(tmp2))
colnames(y.90.R1.SR1.pruned.longform) <- "repeatedseq" 

#--------------------------------------------------
tmp1 <- list()
tmp2 <- list()
for (i in 1:length(pruned.merged.tab.all$y.90.R2.SR3.TR1))
{
  tmp1 <- rep(as.character(pruned.merged.tab.all$seq[i]), pruned.merged.tab.all$y.90.R2.SR3.TR1[i])
  tmp2[[i]] <- tmp1
}
y.90.R2.SR3.TR1.pruned.longform <- as.data.frame(unlist(tmp2))
colnames(y.90.R2.SR3.TR1.pruned.longform) <- "repeatedseq" 

#--------------------------------------------------
tmp1 <- list()
tmp2 <- list()
for (i in 1:length(pruned.merged.tab.all$y.90.R2.SR3.TR2))
{
  tmp1 <- rep(as.character(pruned.merged.tab.all$seq[i]), pruned.merged.tab.all$y.90.R2.SR3.TR2[i])
  tmp2[[i]] <- tmp1
}
y.90.R2.SR3.TR2.pruned.longform <- as.data.frame(unlist(tmp2))
colnames(y.90.R2.SR3.TR2.pruned.longform) <- "repeatedseq" 

#--------------------------------------------------
tmp1 <- list()
tmp2 <- list()
for (i in 1:length(pruned.merged.tab.all$y.90.R3.SR3.TR1))
{
  tmp1 <- rep(as.character(pruned.merged.tab.all$seq[i]), pruned.merged.tab.all$y.90.R3.SR3.TR1[i])
  tmp2[[i]] <- tmp1
}
y.90.R3.SR3.TR1.pruned.longform <- as.data.frame(unlist(tmp2))
colnames(y.90.R3.SR3.TR1.pruned.longform) <- "repeatedseq" 

#--------------------------------------------------
tmp1 <- list()
tmp2 <- list()
for (i in 1:length(pruned.merged.tab.all$y.90.R3.SR3.TR2))
{
  tmp1 <- rep(as.character(pruned.merged.tab.all$seq[i]), pruned.merged.tab.all$y.90.R3.SR3.TR2[i])
  tmp2[[i]] <- tmp1
}
y.90.R3.SR3.TR2.pruned.longform <- as.data.frame(unlist(tmp2))
colnames(y.90.R3.SR3.TR2.pruned.longform) <- "repeatedseq" 

#--------------------------------------------------
tmp1 <- list()
tmp2 <- list()
for (i in 1:length(pruned.merged.tab.all$y.90.R4.SR3.TR1))
{
  tmp1 <- rep(as.character(pruned.merged.tab.all$seq[i]), pruned.merged.tab.all$y.90.R4.SR3.TR1[i])
  tmp2[[i]] <- tmp1
}
y.90.R4.SR3.TR1.pruned.longform <- as.data.frame(unlist(tmp2))
colnames(y.90.R4.SR3.TR1.pruned.longform) <- "repeatedseq" 

#--------------------------------------------------
tmp1 <- list()
tmp2 <- list()
for (i in 1:length(pruned.merged.tab.all$y.90.R4.SR3.TR2))
{
  tmp1 <- rep(as.character(pruned.merged.tab.all$seq[i]), pruned.merged.tab.all$y.90.R4.SR3.TR2[i])
  tmp2[[i]] <- tmp1
}
y.90.R4.SR3.TR2.pruned.longform <- as.data.frame(unlist(tmp2))
colnames(y.90.R4.SR3.TR2.pruned.longform) <- "repeatedseq" 

#--------------------------------------------------
tmp1 <- list()
tmp2 <- list()
for (i in 1:length(pruned.merged.tab.all$y.90.R5.SR3.TR1))
{
  tmp1 <- rep(as.character(pruned.merged.tab.all$seq[i]), pruned.merged.tab.all$y.90.R5.SR3.TR1[i])
  tmp2[[i]] <- tmp1
}
y.90.R5.SR3.TR1.pruned.longform <- as.data.frame(unlist(tmp2))
colnames(y.90.R5.SR3.TR1.pruned.longform) <- "repeatedseq"

#--------------------------------------------------
tmp1 <- list()
tmp2 <- list()
for (i in 1:length(pruned.merged.tab.all$y.90.R5.SR3.TR2))
{
  tmp1 <- rep(as.character(pruned.merged.tab.all$seq[i]), pruned.merged.tab.all$y.90.R5.SR3.TR2[i])
  tmp2[[i]] <- tmp1
}
y.90.R5.SR3.TR2.pruned.longform <- as.data.frame(unlist(tmp2))
colnames(y.90.R5.SR3.TR2.pruned.longform) <- "repeatedseq"

#--------------------------------------------------
tmp1 <- list()
tmp2 <- list()
for (i in 1:length(pruned.merged.tab.all$y.30.R1.SR1))
{
  tmp1 <- rep(as.character(pruned.merged.tab.all$seq[i]), pruned.merged.tab.all$y.30.R1.SR1[i])
  tmp2[[i]] <- tmp1
}
y.30.R1.SR1.pruned.longform <- as.data.frame(unlist(tmp2))
colnames(y.30.R1.SR1.pruned.longform) <- "repeatedseq"

#--------------------------------------------------
tmp1 <- list()
tmp2 <- list()
for (i in 1:length(pruned.merged.tab.all$y.30.R2.SR2))
{
  tmp1 <- rep(as.character(pruned.merged.tab.all$seq[i]), pruned.merged.tab.all$y.30.R2.SR2[i])
  tmp2[[i]] <- tmp1
}
y.30.R2.SR2.pruned.longform <- as.data.frame(unlist(tmp2))
colnames(y.30.R2.SR2.pruned.longform) <- "repeatedseq"

#--------------------------------------------------
tmp1 <- list()
tmp2 <- list()
for (i in 1:length(pruned.merged.tab.all$y.30.R3.SR2))
{
  tmp1 <- rep(as.character(pruned.merged.tab.all$seq[i]), pruned.merged.tab.all$y.30.R3.SR2[i])
  tmp2[[i]] <- tmp1
}
y.30.R3.SR2.pruned.longform <- as.data.frame(unlist(tmp2))
colnames(y.30.R3.SR2.pruned.longform) <- "repeatedseq"

#--------------------------------------------------
tmp1 <- list()
tmp2 <- list()
for (i in 1:length(pruned.merged.tab.all$y.30.R4.SR3.TR1))
{
  tmp1 <- rep(as.character(pruned.merged.tab.all$seq[i]), pruned.merged.tab.all$y.30.R4.SR3.TR1[i])
  tmp2[[i]] <- tmp1
}
y.30.R4.SR3.TR1.pruned.longform <- as.data.frame(unlist(tmp2))
colnames(y.30.R4.SR3.TR1.pruned.longform) <- "repeatedseq"

#--------------------------------------------------
tmp1 <- list()
tmp2 <- list()
for (i in 1:length(pruned.merged.tab.all$y.30.R4.SR3.TR2))
{
  tmp1 <- rep(as.character(pruned.merged.tab.all$seq[i]), pruned.merged.tab.all$y.30.R4.SR3.TR2[i])
  tmp2[[i]] <- tmp1
}
y.30.R4.SR3.TR2.pruned.longform <- as.data.frame(unlist(tmp2))
colnames(y.30.R4.SR3.TR2.pruned.longform) <- "repeatedseq"

#--------------------------------------------------
tmp1 <- list()
tmp2 <- list()
for (i in 1:length(pruned.merged.tab.all$y.30.R5.SR3.TR1))
{
  tmp1 <- rep(as.character(pruned.merged.tab.all$seq[i]), pruned.merged.tab.all$y.30.R5.SR3.TR1[i])
  tmp2[[i]] <- tmp1
}
y.30.R5.SR3.TR1.pruned.longform <- as.data.frame(unlist(tmp2))
colnames(y.30.R5.SR3.TR1.pruned.longform) <- "repeatedseq"

#--------------------------------------------------
tmp1 <- list()
tmp2 <- list()
for (i in 1:length(pruned.merged.tab.all$y.30.R5.SR3.TR2))
{
  tmp1 <- rep(as.character(pruned.merged.tab.all$seq[i]), pruned.merged.tab.all$y.30.R5.SR3.TR2[i])
  tmp2[[i]] <- tmp1
}
y.30.R5.SR3.TR2.pruned.longform <- as.data.frame(unlist(tmp2))
colnames(y.30.R5.SR3.TR2.pruned.longform) <- "repeatedseq"

#--------------------------------------------------
tmp1 <- list()
tmp2 <- list()
for (i in 1:length(pruned.merged.tab.all$y.30.R6.SR3.TR1))
{
  tmp1 <- rep(as.character(pruned.merged.tab.all$seq[i]), pruned.merged.tab.all$y.30.R6.SR3.TR1[i])
  tmp2[[i]] <- tmp1
}
y.30.R6.SR3.TR1.pruned.longform <- as.data.frame(unlist(tmp2))
colnames(y.30.R6.SR3.TR1.pruned.longform) <- "repeatedseq"

#--------------------------------------------------
tmp1 <- list()
tmp2 <- list()
for (i in 1:length(pruned.merged.tab.all$y.30.R6.SR3.TR2))
{
  tmp1 <- rep(as.character(pruned.merged.tab.all$seq[i]), pruned.merged.tab.all$y.30.R6.SR3.TR2[i])
  tmp2[[i]] <- tmp1
}
y.30.R6.SR3.TR2.pruned.longform <- as.data.frame(unlist(tmp2))
colnames(y.30.R6.SR3.TR2.pruned.longform) <- "repeatedseq"

#--------------------------------------------------
tmp1 <- list()
tmp2 <- list()
for (i in 1:length(pruned.merged.tab.all$y.30.R7.SR3.TR1))
{
  tmp1 <- rep(as.character(pruned.merged.tab.all$seq[i]), pruned.merged.tab.all$y.30.R7.SR3.TR1[i])
  tmp2[[i]] <- tmp1
}
y.30.R7.SR3.TR1.pruned.longform <- as.data.frame(unlist(tmp2))
colnames(y.30.R7.SR3.TR1.pruned.longform) <- "repeatedseq"

#--------------------------------------------------
tmp1 <- list()
tmp2 <- list()
for (i in 1:length(pruned.merged.tab.all$y.30.R7.SR3.TR2))
{
  tmp1 <- rep(as.character(pruned.merged.tab.all$seq[i]), pruned.merged.tab.all$y.30.R7.SR3.TR2[i])
  tmp2[[i]] <- tmp1
}
y.30.R7.SR3.TR2.pruned.longform <- as.data.frame(unlist(tmp2))
colnames(y.30.R7.SR3.TR2.pruned.longform) <- "repeatedseq"

#--------------------------------------------------
tmp1 <- list()
tmp2 <- list()
for (i in 1:length(pruned.merged.tab.all$a.30.R1.SR1))
{
  tmp1 <- rep(as.character(pruned.merged.tab.all$seq[i]), pruned.merged.tab.all$a.30.R1.SR1[i])
  tmp2[[i]] <- tmp1
}
a.30.R1.SR1.pruned.longform <- as.data.frame(unlist(tmp2))
colnames(a.30.R1.SR1.pruned.longform) <- "repeatedseq"

#--------------------------------------------------
tmp1 <- list()
tmp2 <- list()
for (i in 1:length(pruned.merged.tab.all$a.30.R2.SR1))
{
  tmp1 <- rep(as.character(pruned.merged.tab.all$seq[i]), pruned.merged.tab.all$a.30.R2.SR1[i])
  tmp2[[i]] <- tmp1
}
a.30.R2.SR1.pruned.longform <- as.data.frame(unlist(tmp2))
colnames(a.30.R2.SR1.pruned.longform) <- "repeatedseq"

#--------------------------------------------------
tmp1 <- list()
tmp2 <- list()
for (i in 1:length(pruned.merged.tab.all$a.30.R3.SR1))
{
  tmp1 <- rep(as.character(pruned.merged.tab.all$seq[i]), pruned.merged.tab.all$a.30.R3.SR1[i])
  tmp2[[i]] <- tmp1
}
a.30.R3.SR1.pruned.longform <- as.data.frame(unlist(tmp2))
colnames(a.30.R3.SR1.pruned.longform) <- "repeatedseq"

#--------------------------------------------------
tmp1 <- list()
tmp2 <- list()
for (i in 1:length(pruned.merged.tab.all$a.30.R4.SR2))
{
  tmp1 <- rep(as.character(pruned.merged.tab.all$seq[i]), pruned.merged.tab.all$a.30.R4.SR2[i])
  tmp2[[i]] <- tmp1
}
a.30.R4.SR2.pruned.longform <- as.data.frame(unlist(tmp2))
colnames(a.30.R4.SR2.pruned.longform) <- "repeatedseq"

#--------------------------------------------------
tmp1 <- list()
tmp2 <- list()
for (i in 1:length(pruned.merged.tab.all$a.30.R5.SR2))
{
  tmp1 <- rep(as.character(pruned.merged.tab.all$seq[i]), pruned.merged.tab.all$a.30.R5.SR2[i])
  tmp2[[i]] <- tmp1
}
a.30.R5.SR2.pruned.longform <- as.data.frame(unlist(tmp2))
colnames(a.30.R5.SR2.pruned.longform) <- "repeatedseq"

#--------------------------------------------------
tmp1 <- list()
tmp2 <- list()
for (i in 1:length(pruned.merged.tab.all$a.30.R6.SR2))
{
  tmp1 <- rep(as.character(pruned.merged.tab.all$seq[i]), pruned.merged.tab.all$a.30.R6.SR2[i])
  tmp2[[i]] <- tmp1
}
a.30.R6.SR2.pruned.longform <- as.data.frame(unlist(tmp2))
colnames(a.30.R6.SR2.pruned.longform) <- "repeatedseq"

#--------------------------------------------------
tmp1 <- list()
tmp2 <- list()
for (i in 1:length(pruned.merged.tab.all$a.30.R7.SR2))
{
  tmp1 <- rep(as.character(pruned.merged.tab.all$seq[i]), pruned.merged.tab.all$a.30.R7.SR2[i])
  tmp2[[i]] <- tmp1
}
a.30.R7.SR2.pruned.longform <- as.data.frame(unlist(tmp2))
colnames(a.30.R7.SR2.pruned.longform) <- "repeatedseq"

#--------------------------------------------------
tmp1 <- list()
tmp2 <- list()
for (i in 1:length(pruned.merged.tab.all$a.30.R8.SR2))
{
  tmp1 <- rep(as.character(pruned.merged.tab.all$seq[i]), pruned.merged.tab.all$a.30.R8.SR2[i])
  tmp2[[i]] <- tmp1
}
a.30.R8.SR2.pruned.longform <- as.data.frame(unlist(tmp2))
colnames(a.30.R8.SR2.pruned.longform) <- "repeatedseq"

#--------------------------------------------------
tmp1 <- list()
tmp2 <- list()
for (i in 1:length(pruned.merged.tab.all$a.30.R9.SR3.TR1))
{
  tmp1 <- rep(as.character(pruned.merged.tab.all$seq[i]), pruned.merged.tab.all$a.30.R9.SR3.TR1[i])
  tmp2[[i]] <- tmp1
}
a.30.R9.SR3.TR1.pruned.longform <- as.data.frame(unlist(tmp2))
colnames(a.30.R9.SR3.TR1.pruned.longform) <- "repeatedseq"

#--------------------------------------------------
tmp1 <- list()
tmp2 <- list()
for (i in 1:length(pruned.merged.tab.all$a.30.R9.SR3.TR2))
{
  tmp1 <- rep(as.character(pruned.merged.tab.all$seq[i]), pruned.merged.tab.all$a.30.R9.SR3.TR2[i])
  tmp2[[i]] <- tmp1
}
a.30.R9.SR3.TR2.pruned.longform <- as.data.frame(unlist(tmp2))
colnames(a.30.R9.SR3.TR2.pruned.longform) <- "repeatedseq"

#--------------------------------------------------
tmp1 <- list()
tmp2 <- list()
for (i in 1:length(pruned.merged.tab.all$a.30.R10.SR3.TR1))
{
  tmp1 <- rep(as.character(pruned.merged.tab.all$seq[i]), pruned.merged.tab.all$a.30.R10.SR3.TR1[i])
  tmp2[[i]] <- tmp1
}
a.30.R10.SR3.TR1.pruned.longform <- as.data.frame(unlist(tmp2))
colnames(a.30.R10.SR3.TR1.pruned.longform) <- "repeatedseq"

#--------------------------------------------------
tmp1 <- list()
tmp2 <- list()
for (i in 1:length(pruned.merged.tab.all$a.30.R10.SR3.TR2))
{
  tmp1 <- rep(as.character(pruned.merged.tab.all$seq[i]), pruned.merged.tab.all$a.30.R10.SR3.TR2[i])
  tmp2[[i]] <- tmp1
}
a.30.R10.SR3.TR2.pruned.longform <- as.data.frame(unlist(tmp2))
colnames(a.30.R10.SR3.TR2.pruned.longform) <- "repeatedseq"
```

```{r}
#------------------------------------------------------------------
rep.seq.vec <- DF1.R1.SR1.pruned.longform # Change here for each sample
colnames(rep.seq.vec) <- "rep.seq"
tmp1.list <- list()
for (i in 1:500)
{
  rep.seq.df <- as.data.frame(rep.seq.vec$rep.seq)
  tmp1 <- sample(rep.seq.df$`rep.seq.vec$rep.seq`, 2400, replace = T)
  tmp1.list[[i]] <- tmp1
}
      tmp1.df <- data.frame()
      tmp2.df <- matrix(nrow = 2400, ncol = 500)
      for (j in 1:2400)
      {
          for (i in 1:500)
          {
          tmp1.df <- as.data.frame(unlist(tmp1.list[[i]]))
          tmp2.df[j,i] <- as.character(tmp1.df[j,1])
          }
      }
            length.unique.list <- list()
            tab.1 <- data.frame()
            freq.tmp <- data.frame()
            tmp2.tab <- list()
            for (i in 1:500)
            {
              tab.1 <- as.data.frame(table(tmp2.df[,i]))
              freq.tmp <- tab.1$Freq
              length.unique.list[i] <- length(tab.1[,1])
              tmp2.tab[[i]] <- freq.tmp 
            }
            collength = 5 
            cutoff.val = 50
            tmp1 <- matrix(ncol = collength, nrow = 500) 
                        for (i in 1:500)
                        {
                          tmp1[i,1] <- length(which(tmp2.tab[[i]] > cutoff.val)) #HDP initial
                          tmp1[i,2] <- length(which(tmp2.tab[[i]] < cutoff.val & tmp2.tab[[i]] > 0)) #LDP initial
                          tmp1[i,3] <- sum(tmp2.tab[[i]][tmp2.tab[[i]]>cutoff.val]) #HDP final
                          tmp1[i,4] <- sum(tmp2.tab[[i]][tmp2.tab[[i]]<cutoff.val]) #LDP final
                          tmp1[i,5] <- as.numeric(unlist(length.unique.list[[i]]))
                        }
            DF1.R1.SR1.bootstrap.pruned <- tmp1 # Change here for each sample

            
#------------------------------------------------------------------
rep.seq.vec <- DF1.R2.SR3.TR1.pruned.longform # Change here for each sample
colnames(rep.seq.vec) <- "rep.seq"
tmp1.list <- list()
for (i in 1:500)
{
  rep.seq.df <- as.data.frame(rep.seq.vec$rep.seq)
  tmp1 <- sample(rep.seq.df$`rep.seq.vec$rep.seq`, 9000, replace = T)
  tmp1.list[[i]] <- tmp1
}
      tmp1.df <- data.frame()
      tmp2.df <- matrix(nrow = 9000, ncol = 500)
      for (j in 1:9000)
      {
          for (i in 1:500)
          {
          tmp1.df <- as.data.frame(unlist(tmp1.list[[i]]))
          tmp2.df[j,i] <- as.character(tmp1.df[j,1])
          }
      }
            length.unique.list <- list()
            tab.1 <- data.frame()
            freq.tmp <- data.frame()
            tmp2.tab <- list()
            for (i in 1:500)
            {
              tab.1 <- as.data.frame(table(tmp2.df[,i]))
              freq.tmp <- tab.1$Freq
              length.unique.list[i] <- length(tab.1[,1])
              tmp2.tab[[i]] <- freq.tmp 
            }
            collength = 5 
            cutoff.val = 50
            tmp1 <- matrix(ncol = collength, nrow = 500) 
                        for (i in 1:500)
                        {
                          tmp1[i,1] <- length(which(tmp2.tab[[i]] > cutoff.val)) #HDP initial
                          tmp1[i,2] <- length(which(tmp2.tab[[i]] < cutoff.val & tmp2.tab[[i]] > 0)) #LDP initial
                          tmp1[i,3] <- sum(tmp2.tab[[i]][tmp2.tab[[i]]>cutoff.val]) #HDP final
                          tmp1[i,4] <- sum(tmp2.tab[[i]][tmp2.tab[[i]]<cutoff.val]) #LDP final
                          tmp1[i,5] <- as.numeric(unlist(length.unique.list[[i]]))
                        }
            DF1.R2.SR3.TR1.bootstrap.pruned <- tmp1 # Change here for each sample
            
#------------------------------------------------------------------
rep.seq.vec <- DF1.R2.SR3.TR2.pruned.longform # Change here for each sample
colnames(rep.seq.vec) <- "rep.seq"
tmp1.list <- list()
for (i in 1:500)
{
  rep.seq.df <- as.data.frame(rep.seq.vec$rep.seq)
  tmp1 <- sample(rep.seq.df$`rep.seq.vec$rep.seq`, 9000, replace = T)
  tmp1.list[[i]] <- tmp1
}
      tmp1.df <- data.frame()
      tmp2.df <- matrix(nrow = 9000, ncol = 500)
      for (j in 1:9000)
      {
          for (i in 1:500)
          {
          tmp1.df <- as.data.frame(unlist(tmp1.list[[i]]))
          tmp2.df[j,i] <- as.character(tmp1.df[j,1])
          }
      }
            length.unique.list <- list()
            tab.1 <- data.frame()
            freq.tmp <- data.frame()
            tmp2.tab <- list()
            for (i in 1:500)
            {
              tab.1 <- as.data.frame(table(tmp2.df[,i]))
              freq.tmp <- tab.1$Freq
              length.unique.list[i] <- length(tab.1[,1])
              tmp2.tab[[i]] <- freq.tmp 
            }
            collength = 5 
            cutoff.val = 50
            tmp1 <- matrix(ncol = collength, nrow = 500) 
                        for (i in 1:500)
                        {
                          tmp1[i,1] <- length(which(tmp2.tab[[i]] > cutoff.val)) #HDP initial
                          tmp1[i,2] <- length(which(tmp2.tab[[i]] < cutoff.val & tmp2.tab[[i]] > 0)) #LDP initial
                          tmp1[i,3] <- sum(tmp2.tab[[i]][tmp2.tab[[i]]>cutoff.val]) #HDP final
                          tmp1[i,4] <- sum(tmp2.tab[[i]][tmp2.tab[[i]]<cutoff.val]) #LDP final
                          tmp1[i,5] <- as.numeric(unlist(length.unique.list[[i]]))
                        }
            DF1.R2.SR3.TR2.bootstrap.pruned <- tmp1 # Change here for each sample
            
#------------------------------------------------------------------
rep.seq.vec <- y.90.R1.SR1.pruned.longform # Change here for each sample
colnames(rep.seq.vec) <- "rep.seq"
tmp1.list <- list()
for (i in 1:500)
{
  rep.seq.df <- as.data.frame(rep.seq.vec$rep.seq)
  tmp1 <- sample(rep.seq.df$`rep.seq.vec$rep.seq`, 2400, replace = T)
  tmp1.list[[i]] <- tmp1
}
      tmp1.df <- data.frame()
      tmp2.df <- matrix(nrow = 2400, ncol = 500)
      for (j in 1:2400)
      {
          for (i in 1:500)
          {
          tmp1.df <- as.data.frame(unlist(tmp1.list[[i]]))
          tmp2.df[j,i] <- as.character(tmp1.df[j,1])
          }
      }
            length.unique.list <- list()
            tab.1 <- data.frame()
            freq.tmp <- data.frame()
            tmp2.tab <- list()
            for (i in 1:500)
            {
              tab.1 <- as.data.frame(table(tmp2.df[,i]))
              freq.tmp <- tab.1$Freq
              length.unique.list[i] <- length(tab.1[,1])
              tmp2.tab[[i]] <- freq.tmp 
            }
            collength = 5 
            cutoff.val = 50
            tmp1 <- matrix(ncol = collength, nrow = 500) 
                        for (i in 1:500)
                        {
                          tmp1[i,1] <- length(which(tmp2.tab[[i]] > cutoff.val)) #HDP initial
                          tmp1[i,2] <- length(which(tmp2.tab[[i]] < cutoff.val & tmp2.tab[[i]] > 0)) #LDP initial
                          tmp1[i,3] <- sum(tmp2.tab[[i]][tmp2.tab[[i]]>cutoff.val]) #HDP final
                          tmp1[i,4] <- sum(tmp2.tab[[i]][tmp2.tab[[i]]<cutoff.val]) #LDP final
                          tmp1[i,5] <- as.numeric(unlist(length.unique.list[[i]]))
                        }
            y.90.R1.SR1.bootstrap.pruned <- tmp1 # Change here for each sample
            
#------------------------------------------------------------------
rep.seq.vec <- y.90.R2.SR3.TR1.pruned.longform # Change here for each sample
colnames(rep.seq.vec) <- "rep.seq"
tmp1.list <- list()
for (i in 1:500)
{
  rep.seq.df <- as.data.frame(rep.seq.vec$rep.seq)
  tmp1 <- sample(rep.seq.df$`rep.seq.vec$rep.seq`, 9000, replace = T)
  tmp1.list[[i]] <- tmp1
}
      tmp1.df <- data.frame()
      tmp2.df <- matrix(nrow = 9000, ncol = 500)
      for (j in 1:9000)
      {
          for (i in 1:500)
          {
          tmp1.df <- as.data.frame(unlist(tmp1.list[[i]]))
          tmp2.df[j,i] <- as.character(tmp1.df[j,1])
          }
      }
            length.unique.list <- list()
            tab.1 <- data.frame()
            freq.tmp <- data.frame()
            tmp2.tab <- list()
            for (i in 1:500)
            {
              tab.1 <- as.data.frame(table(tmp2.df[,i]))
              freq.tmp <- tab.1$Freq
              length.unique.list[i] <- length(tab.1[,1])
              tmp2.tab[[i]] <- freq.tmp 
            }
            collength = 5 
            cutoff.val = 50
            tmp1 <- matrix(ncol = collength, nrow = 500) 
                        for (i in 1:500)
                        {
                          tmp1[i,1] <- length(which(tmp2.tab[[i]] > cutoff.val)) #HDP initial
                          tmp1[i,2] <- length(which(tmp2.tab[[i]] < cutoff.val & tmp2.tab[[i]] > 0)) #LDP initial
                          tmp1[i,3] <- sum(tmp2.tab[[i]][tmp2.tab[[i]]>cutoff.val]) #HDP final
                          tmp1[i,4] <- sum(tmp2.tab[[i]][tmp2.tab[[i]]<cutoff.val]) #LDP final
                          tmp1[i,5] <- as.numeric(unlist(length.unique.list[[i]]))
                        }
            y.90.R2.SR3.TR1.bootstrap.pruned <- tmp1 # Change here for each sample
            
#------------------------------------------------------------------
rep.seq.vec <- y.90.R2.SR3.TR2.pruned.longform # Change here for each sample
colnames(rep.seq.vec) <- "rep.seq"
tmp1.list <- list()
for (i in 1:500)
{
  rep.seq.df <- as.data.frame(rep.seq.vec$rep.seq)
  tmp1 <- sample(rep.seq.df$`rep.seq.vec$rep.seq`, 9000, replace = T)
  tmp1.list[[i]] <- tmp1
}
      tmp1.df <- data.frame()
      tmp2.df <- matrix(nrow = 9000, ncol = 500)
      for (j in 1:9000)
      {
          for (i in 1:500)
          {
          tmp1.df <- as.data.frame(unlist(tmp1.list[[i]]))
          tmp2.df[j,i] <- as.character(tmp1.df[j,1])
          }
      }
            length.unique.list <- list()
            tab.1 <- data.frame()
            freq.tmp <- data.frame()
            tmp2.tab <- list()
            for (i in 1:500)
            {
              tab.1 <- as.data.frame(table(tmp2.df[,i]))
              freq.tmp <- tab.1$Freq
              length.unique.list[i] <- length(tab.1[,1])
              tmp2.tab[[i]] <- freq.tmp 
            }
            collength = 5 
            cutoff.val = 50
            tmp1 <- matrix(ncol = collength, nrow = 500) 
                        for (i in 1:500)
                        {
                          tmp1[i,1] <- length(which(tmp2.tab[[i]] > cutoff.val)) #HDP initial
                          tmp1[i,2] <- length(which(tmp2.tab[[i]] < cutoff.val & tmp2.tab[[i]] > 0)) #LDP initial
                          tmp1[i,3] <- sum(tmp2.tab[[i]][tmp2.tab[[i]]>cutoff.val]) #HDP final
                          tmp1[i,4] <- sum(tmp2.tab[[i]][tmp2.tab[[i]]<cutoff.val]) #LDP final
                          tmp1[i,5] <- as.numeric(unlist(length.unique.list[[i]]))
                        }
            y.90.R2.SR3.TR2.bootstrap.pruned <- tmp1 # Change here for each sample

#------------------------------------------------------------------
rep.seq.vec <- y.90.R3.SR3.TR1.pruned.longform # Change here for each sample
colnames(rep.seq.vec) <- "rep.seq"
tmp1.list <- list()
for (i in 1:500)
{
  rep.seq.df <- as.data.frame(rep.seq.vec$rep.seq)
  tmp1 <- sample(rep.seq.df$`rep.seq.vec$rep.seq`, 9000, replace = T)
  tmp1.list[[i]] <- tmp1
}
      tmp1.df <- data.frame()
      tmp2.df <- matrix(nrow = 9000, ncol = 500)
      for (j in 1:9000)
      {
          for (i in 1:500)
          {
          tmp1.df <- as.data.frame(unlist(tmp1.list[[i]]))
          tmp2.df[j,i] <- as.character(tmp1.df[j,1])
          }
      }
            length.unique.list <- list()
            tab.1 <- data.frame()
            freq.tmp <- data.frame()
            tmp2.tab <- list()
            for (i in 1:500)
            {
              tab.1 <- as.data.frame(table(tmp2.df[,i]))
              freq.tmp <- tab.1$Freq
              length.unique.list[i] <- length(tab.1[,1])
              tmp2.tab[[i]] <- freq.tmp 
            }
            collength = 5 
            cutoff.val = 50
            tmp1 <- matrix(ncol = collength, nrow = 500) 
                        for (i in 1:500)
                        {
                          tmp1[i,1] <- length(which(tmp2.tab[[i]] > cutoff.val)) #HDP initial
                          tmp1[i,2] <- length(which(tmp2.tab[[i]] < cutoff.val & tmp2.tab[[i]] > 0)) #LDP initial
                          tmp1[i,3] <- sum(tmp2.tab[[i]][tmp2.tab[[i]]>cutoff.val]) #HDP final
                          tmp1[i,4] <- sum(tmp2.tab[[i]][tmp2.tab[[i]]<cutoff.val]) #LDP final
                          tmp1[i,5] <- as.numeric(unlist(length.unique.list[[i]]))
                        }
            y.90.R3.SR3.TR1.bootstrap.pruned <- tmp1 # Change here for each sample

#------------------------------------------------------------------
rep.seq.vec <- y.90.R3.SR3.TR2.pruned.longform # Change here for each sample
colnames(rep.seq.vec) <- "rep.seq"
tmp1.list <- list()
for (i in 1:500)
{
  rep.seq.df <- as.data.frame(rep.seq.vec$rep.seq)
  tmp1 <- sample(rep.seq.df$`rep.seq.vec$rep.seq`, 9000, replace = T)
  tmp1.list[[i]] <- tmp1
}
      tmp1.df <- data.frame()
      tmp2.df <- matrix(nrow = 9000, ncol = 500)
      for (j in 1:9000)
      {
          for (i in 1:500)
          {
          tmp1.df <- as.data.frame(unlist(tmp1.list[[i]]))
          tmp2.df[j,i] <- as.character(tmp1.df[j,1])
          }
      }
            length.unique.list <- list()
            tab.1 <- data.frame()
            freq.tmp <- data.frame()
            tmp2.tab <- list()
            for (i in 1:500)
            {
              tab.1 <- as.data.frame(table(tmp2.df[,i]))
              freq.tmp <- tab.1$Freq
              length.unique.list[i] <- length(tab.1[,1])
              tmp2.tab[[i]] <- freq.tmp 
            }
            collength = 5 
            cutoff.val = 50
            tmp1 <- matrix(ncol = collength, nrow = 500) 
                        for (i in 1:500)
                        {
                          tmp1[i,1] <- length(which(tmp2.tab[[i]] > cutoff.val)) #HDP initial
                          tmp1[i,2] <- length(which(tmp2.tab[[i]] < cutoff.val & tmp2.tab[[i]] > 0)) #LDP initial
                          tmp1[i,3] <- sum(tmp2.tab[[i]][tmp2.tab[[i]]>cutoff.val]) #HDP final
                          tmp1[i,4] <- sum(tmp2.tab[[i]][tmp2.tab[[i]]<cutoff.val]) #LDP final
                          tmp1[i,5] <- as.numeric(unlist(length.unique.list[[i]]))
                        }
            y.90.R3.SR3.TR2.bootstrap.pruned <- tmp1 # Change here for each sample
            
#------------------------------------------------------------------
rep.seq.vec <- y.90.R4.SR3.TR1.pruned.longform # Change here for each sample
colnames(rep.seq.vec) <- "rep.seq"
tmp1.list <- list()
for (i in 1:500)
{
  rep.seq.df <- as.data.frame(rep.seq.vec$rep.seq)
  tmp1 <- sample(rep.seq.df$`rep.seq.vec$rep.seq`, 9000, replace = T)
  tmp1.list[[i]] <- tmp1
}
      tmp1.df <- data.frame()
      tmp2.df <- matrix(nrow = 9000, ncol = 500)
      for (j in 1:9000)
      {
          for (i in 1:500)
          {
          tmp1.df <- as.data.frame(unlist(tmp1.list[[i]]))
          tmp2.df[j,i] <- as.character(tmp1.df[j,1])
          }
      }
            length.unique.list <- list()
            tab.1 <- data.frame()
            freq.tmp <- data.frame()
            tmp2.tab <- list()
            for (i in 1:500)
            {
              tab.1 <- as.data.frame(table(tmp2.df[,i]))
              freq.tmp <- tab.1$Freq
              length.unique.list[i] <- length(tab.1[,1])
              tmp2.tab[[i]] <- freq.tmp 
            }
            collength = 5 
            cutoff.val = 50
            tmp1 <- matrix(ncol = collength, nrow = 500) 
                        for (i in 1:500)
                        {
                          tmp1[i,1] <- length(which(tmp2.tab[[i]] > cutoff.val)) #HDP initial
                          tmp1[i,2] <- length(which(tmp2.tab[[i]] < cutoff.val & tmp2.tab[[i]] > 0)) #LDP initial
                          tmp1[i,3] <- sum(tmp2.tab[[i]][tmp2.tab[[i]]>cutoff.val]) #HDP final
                          tmp1[i,4] <- sum(tmp2.tab[[i]][tmp2.tab[[i]]<cutoff.val]) #LDP final
                          tmp1[i,5] <- as.numeric(unlist(length.unique.list[[i]]))
                        }
            y.90.R4.SR3.TR1.bootstrap.pruned <- tmp1 # Change here for each sample
            
#------------------------------------------------------------------
rep.seq.vec <- y.90.R4.SR3.TR2.pruned.longform # Change here for each sample
colnames(rep.seq.vec) <- "rep.seq"
tmp1.list <- list()
for (i in 1:500)
{
  rep.seq.df <- as.data.frame(rep.seq.vec$rep.seq)
  tmp1 <- sample(rep.seq.df$`rep.seq.vec$rep.seq`, 9000, replace = T)
  tmp1.list[[i]] <- tmp1
}
      tmp1.df <- data.frame()
      tmp2.df <- matrix(nrow = 9000, ncol = 500)
      for (j in 1:9000)
      {
          for (i in 1:500)
          {
          tmp1.df <- as.data.frame(unlist(tmp1.list[[i]]))
          tmp2.df[j,i] <- as.character(tmp1.df[j,1])
          }
      }
            length.unique.list <- list()
            tab.1 <- data.frame()
            freq.tmp <- data.frame()
            tmp2.tab <- list()
            for (i in 1:500)
            {
              tab.1 <- as.data.frame(table(tmp2.df[,i]))
              freq.tmp <- tab.1$Freq
              length.unique.list[i] <- length(tab.1[,1])
              tmp2.tab[[i]] <- freq.tmp 
            }
            collength = 5 
            cutoff.val = 50
            tmp1 <- matrix(ncol = collength, nrow = 500) 
                        for (i in 1:500)
                        {
                          tmp1[i,1] <- length(which(tmp2.tab[[i]] > cutoff.val)) #HDP initial
                          tmp1[i,2] <- length(which(tmp2.tab[[i]] < cutoff.val & tmp2.tab[[i]] > 0)) #LDP initial
                          tmp1[i,3] <- sum(tmp2.tab[[i]][tmp2.tab[[i]]>cutoff.val]) #HDP final
                          tmp1[i,4] <- sum(tmp2.tab[[i]][tmp2.tab[[i]]<cutoff.val]) #LDP final
                          tmp1[i,5] <- as.numeric(unlist(length.unique.list[[i]]))
                        }
            y.90.R4.SR3.TR2.bootstrap.pruned <- tmp1 # Change here for each sample
            
#------------------------------------------------------------------
rep.seq.vec <- y.90.R5.SR3.TR1.pruned.longform # Change here for each sample
colnames(rep.seq.vec) <- "rep.seq"
tmp1.list <- list()
for (i in 1:500)
{
  rep.seq.df <- as.data.frame(rep.seq.vec$rep.seq)
  tmp1 <- sample(rep.seq.df$`rep.seq.vec$rep.seq`, 9000, replace = T)
  tmp1.list[[i]] <- tmp1
}
      tmp1.df <- data.frame()
      tmp2.df <- matrix(nrow = 9000, ncol = 500)
      for (j in 1:9000)
      {
          for (i in 1:500)
          {
          tmp1.df <- as.data.frame(unlist(tmp1.list[[i]]))
          tmp2.df[j,i] <- as.character(tmp1.df[j,1])
          }
      }
            length.unique.list <- list()
            tab.1 <- data.frame()
            freq.tmp <- data.frame()
            tmp2.tab <- list()
            for (i in 1:500)
            {
              tab.1 <- as.data.frame(table(tmp2.df[,i]))
              freq.tmp <- tab.1$Freq
              length.unique.list[i] <- length(tab.1[,1])
              tmp2.tab[[i]] <- freq.tmp 
            }
            collength = 5 
            cutoff.val = 50
            tmp1 <- matrix(ncol = collength, nrow = 500) 
                        for (i in 1:500)
                        {
                          tmp1[i,1] <- length(which(tmp2.tab[[i]] > cutoff.val)) #HDP initial
                          tmp1[i,2] <- length(which(tmp2.tab[[i]] < cutoff.val & tmp2.tab[[i]] > 0)) #LDP initial
                          tmp1[i,3] <- sum(tmp2.tab[[i]][tmp2.tab[[i]]>cutoff.val]) #HDP final
                          tmp1[i,4] <- sum(tmp2.tab[[i]][tmp2.tab[[i]]<cutoff.val]) #LDP final
                          tmp1[i,5] <- as.numeric(unlist(length.unique.list[[i]]))
                        }
            y.90.R5.SR3.TR1.bootstrap.pruned <- tmp1 # Change here for each sample

#------------------------------------------------------------------
rep.seq.vec <- y.90.R5.SR3.TR2.pruned.longform # Change here for each sample
colnames(rep.seq.vec) <- "rep.seq"
tmp1.list <- list()
for (i in 1:500)
{
  rep.seq.df <- as.data.frame(rep.seq.vec$rep.seq)
  tmp1 <- sample(rep.seq.df$`rep.seq.vec$rep.seq`, 9000, replace = T)
  tmp1.list[[i]] <- tmp1
}
      tmp1.df <- data.frame()
      tmp2.df <- matrix(nrow = 9000, ncol = 500)
      for (j in 1:9000)
      {
          for (i in 1:500)
          {
          tmp1.df <- as.data.frame(unlist(tmp1.list[[i]]))
          tmp2.df[j,i] <- as.character(tmp1.df[j,1])
          }
      }
            length.unique.list <- list()
            tab.1 <- data.frame()
            freq.tmp <- data.frame()
            tmp2.tab <- list()
            for (i in 1:500)
            {
              tab.1 <- as.data.frame(table(tmp2.df[,i]))
              freq.tmp <- tab.1$Freq
              length.unique.list[i] <- length(tab.1[,1])
              tmp2.tab[[i]] <- freq.tmp 
            }
            collength = 5 
            cutoff.val = 50
            tmp1 <- matrix(ncol = collength, nrow = 500) 
                        for (i in 1:500)
                        {
                          tmp1[i,1] <- length(which(tmp2.tab[[i]] > cutoff.val)) #HDP initial
                          tmp1[i,2] <- length(which(tmp2.tab[[i]] < cutoff.val & tmp2.tab[[i]] > 0)) #LDP initial
                          tmp1[i,3] <- sum(tmp2.tab[[i]][tmp2.tab[[i]]>cutoff.val]) #HDP final
                          tmp1[i,4] <- sum(tmp2.tab[[i]][tmp2.tab[[i]]<cutoff.val]) #LDP final
                          tmp1[i,5] <- as.numeric(unlist(length.unique.list[[i]]))
                        }
            y.90.R5.SR3.TR2.bootstrap.pruned <- tmp1 # Change here for each sample

#------------------------------------------------------------------
rep.seq.vec <- y.30.R1.SR1.pruned.longform # Change here for each sample
colnames(rep.seq.vec) <- "rep.seq"
tmp1.list <- list()
for (i in 1:500)
{
  rep.seq.df <- as.data.frame(rep.seq.vec$rep.seq)
  tmp1 <- sample(rep.seq.df$`rep.seq.vec$rep.seq`, 2400, replace = T)
  tmp1.list[[i]] <- tmp1
}
      tmp1.df <- data.frame()
      tmp2.df <- matrix(nrow = 2400, ncol = 500)
      for (j in 1:2400)
      {
          for (i in 1:500)
          {
          tmp1.df <- as.data.frame(unlist(tmp1.list[[i]]))
          tmp2.df[j,i] <- as.character(tmp1.df[j,1])
          }
      }
            length.unique.list <- list()
            tab.1 <- data.frame()
            freq.tmp <- data.frame()
            tmp2.tab <- list()
            for (i in 1:500)
            {
              tab.1 <- as.data.frame(table(tmp2.df[,i]))
              freq.tmp <- tab.1$Freq
              length.unique.list[i] <- length(tab.1[,1])
              tmp2.tab[[i]] <- freq.tmp 
            }
            collength = 5 
            cutoff.val = 50
            tmp1 <- matrix(ncol = collength, nrow = 500) 
                        for (i in 1:500)
                        {
                          tmp1[i,1] <- length(which(tmp2.tab[[i]] > cutoff.val)) #HDP initial
                          tmp1[i,2] <- length(which(tmp2.tab[[i]] < cutoff.val & tmp2.tab[[i]] > 0)) #LDP initial
                          tmp1[i,3] <- sum(tmp2.tab[[i]][tmp2.tab[[i]]>cutoff.val]) #HDP final
                          tmp1[i,4] <- sum(tmp2.tab[[i]][tmp2.tab[[i]]<cutoff.val]) #LDP final
                          tmp1[i,5] <- as.numeric(unlist(length.unique.list[[i]]))
                        }
            y.30.R1.SR1.bootstrap.pruned <- tmp1 # Change here for each sample

            
#------------------------------------------------------------------
rep.seq.vec <- y.30.R2.SR2.pruned.longform # Change here for each sample
colnames(rep.seq.vec) <- "rep.seq"
tmp1.list <- list()
for (i in 1:500)
{
  rep.seq.df <- as.data.frame(rep.seq.vec$rep.seq)
  tmp1 <- sample(rep.seq.df$`rep.seq.vec$rep.seq`, 55000, replace = T)
  tmp1.list[[i]] <- tmp1
}
      tmp1.df <- data.frame()
      tmp2.df <- matrix(nrow = 55000, ncol = 500)
      for (j in 1:55000)
      {
          for (i in 1:500)
          {
          tmp1.df <- as.data.frame(unlist(tmp1.list[[i]]))
          tmp2.df[j,i] <- as.character(tmp1.df[j,1])
          }
      }
            length.unique.list <- list()
            tab.1 <- data.frame()
            freq.tmp <- data.frame()
            tmp2.tab <- list()
            for (i in 1:500)
            {
              tab.1 <- as.data.frame(table(tmp2.df[,i]))
              freq.tmp <- tab.1$Freq
              length.unique.list[i] <- length(tab.1[,1])
              tmp2.tab[[i]] <- freq.tmp 
            }
            collength = 5 
            cutoff.val = 50
            tmp1 <- matrix(ncol = collength, nrow = 500) 
                        for (i in 1:500)
                        {
                          tmp1[i,1] <- length(which(tmp2.tab[[i]] > cutoff.val)) #HDP initial
                          tmp1[i,2] <- length(which(tmp2.tab[[i]] < cutoff.val & tmp2.tab[[i]] > 0)) #LDP initial
                          tmp1[i,3] <- sum(tmp2.tab[[i]][tmp2.tab[[i]]>cutoff.val]) #HDP final
                          tmp1[i,4] <- sum(tmp2.tab[[i]][tmp2.tab[[i]]<cutoff.val]) #LDP final
                          tmp1[i,5] <- as.numeric(unlist(length.unique.list[[i]]))
                        }
            y.30.R2.SR2.bootstrap.pruned <- tmp1 # Change here for each sample

            
#------------------------------------------------------------------
rep.seq.vec <- y.30.R3.SR2.pruned.longform # Change here for each sample
colnames(rep.seq.vec) <- "rep.seq"
tmp1.list <- list()
for (i in 1:500)
{
  rep.seq.df <- as.data.frame(rep.seq.vec$rep.seq)
  tmp1 <- sample(rep.seq.df$`rep.seq.vec$rep.seq`, 55000, replace = T)
  tmp1.list[[i]] <- tmp1
}
      tmp1.df <- data.frame()
      tmp2.df <- matrix(nrow = 55000, ncol = 500)
      for (j in 1:55000)
      {
          for (i in 1:500)
          {
          tmp1.df <- as.data.frame(unlist(tmp1.list[[i]]))
          tmp2.df[j,i] <- as.character(tmp1.df[j,1])
          }
      }
            length.unique.list <- list()
            tab.1 <- data.frame()
            freq.tmp <- data.frame()
            tmp2.tab <- list()
            for (i in 1:500)
            {
              tab.1 <- as.data.frame(table(tmp2.df[,i]))
              freq.tmp <- tab.1$Freq
              length.unique.list[i] <- length(tab.1[,1])
              tmp2.tab[[i]] <- freq.tmp 
            }
            collength = 5 
            cutoff.val = 50
            tmp1 <- matrix(ncol = collength, nrow = 500) 
                        for (i in 1:500)
                        {
                          tmp1[i,1] <- length(which(tmp2.tab[[i]] > cutoff.val)) #HDP initial
                          tmp1[i,2] <- length(which(tmp2.tab[[i]] < cutoff.val & tmp2.tab[[i]] > 0)) #LDP initial
                          tmp1[i,3] <- sum(tmp2.tab[[i]][tmp2.tab[[i]]>cutoff.val]) #HDP final
                          tmp1[i,4] <- sum(tmp2.tab[[i]][tmp2.tab[[i]]<cutoff.val]) #LDP final
                          tmp1[i,5] <- as.numeric(unlist(length.unique.list[[i]]))
                        }
            y.30.R3.SR2.bootstrap.pruned <- tmp1 # Change here for each sample
            
#------------------------------------------------------------------
rep.seq.vec <- y.30.R4.SR3.TR1.pruned.longform # Change here for each sample
colnames(rep.seq.vec) <- "rep.seq"
tmp1.list <- list()
for (i in 1:500)
{
  rep.seq.df <- as.data.frame(rep.seq.vec$rep.seq)
  tmp1 <- sample(rep.seq.df$`rep.seq.vec$rep.seq`, 9000, replace = T)
  tmp1.list[[i]] <- tmp1
}
      tmp1.df <- data.frame()
      tmp2.df <- matrix(nrow = 9000, ncol = 500)
      for (j in 1:9000)
      {
          for (i in 1:500)
          {
          tmp1.df <- as.data.frame(unlist(tmp1.list[[i]]))
          tmp2.df[j,i] <- as.character(tmp1.df[j,1])
          }
      }
            length.unique.list <- list()
            tab.1 <- data.frame()
            freq.tmp <- data.frame()
            tmp2.tab <- list()
            for (i in 1:500)
            {
              tab.1 <- as.data.frame(table(tmp2.df[,i]))
              freq.tmp <- tab.1$Freq
              length.unique.list[i] <- length(tab.1[,1])
              tmp2.tab[[i]] <- freq.tmp 
            }
            collength = 5 
            cutoff.val = 50
            tmp1 <- matrix(ncol = collength, nrow = 500) 
                        for (i in 1:500)
                        {
                          tmp1[i,1] <- length(which(tmp2.tab[[i]] > cutoff.val)) #HDP initial
                          tmp1[i,2] <- length(which(tmp2.tab[[i]] < cutoff.val & tmp2.tab[[i]] > 0)) #LDP initial
                          tmp1[i,3] <- sum(tmp2.tab[[i]][tmp2.tab[[i]]>cutoff.val]) #HDP final
                          tmp1[i,4] <- sum(tmp2.tab[[i]][tmp2.tab[[i]]<cutoff.val]) #LDP final
                          tmp1[i,5] <- as.numeric(unlist(length.unique.list[[i]]))
                        }
            y.30.R4.SR3.TR1.bootstrap.pruned <- tmp1 # Change here for each sample

#------------------------------------------------------------------
rep.seq.vec <- y.30.R4.SR3.TR2.pruned.longform # Change here for each sample
colnames(rep.seq.vec) <- "rep.seq"
tmp1.list <- list()
for (i in 1:500)
{
  rep.seq.df <- as.data.frame(rep.seq.vec$rep.seq)
  tmp1 <- sample(rep.seq.df$`rep.seq.vec$rep.seq`, 9000, replace = T)
  tmp1.list[[i]] <- tmp1
}
      tmp1.df <- data.frame()
      tmp2.df <- matrix(nrow = 9000, ncol = 500)
      for (j in 1:9000)
      {
          for (i in 1:500)
          {
          tmp1.df <- as.data.frame(unlist(tmp1.list[[i]]))
          tmp2.df[j,i] <- as.character(tmp1.df[j,1])
          }
      }
            length.unique.list <- list()
            tab.1 <- data.frame()
            freq.tmp <- data.frame()
            tmp2.tab <- list()
            for (i in 1:500)
            {
              tab.1 <- as.data.frame(table(tmp2.df[,i]))
              freq.tmp <- tab.1$Freq
              length.unique.list[i] <- length(tab.1[,1])
              tmp2.tab[[i]] <- freq.tmp 
            }
            collength = 5 
            cutoff.val = 50
            tmp1 <- matrix(ncol = collength, nrow = 500) 
                        for (i in 1:500)
                        {
                          tmp1[i,1] <- length(which(tmp2.tab[[i]] > cutoff.val)) #HDP initial
                          tmp1[i,2] <- length(which(tmp2.tab[[i]] < cutoff.val & tmp2.tab[[i]] > 0)) #LDP initial
                          tmp1[i,3] <- sum(tmp2.tab[[i]][tmp2.tab[[i]]>cutoff.val]) #HDP final
                          tmp1[i,4] <- sum(tmp2.tab[[i]][tmp2.tab[[i]]<cutoff.val]) #LDP final
                          tmp1[i,5] <- as.numeric(unlist(length.unique.list[[i]]))
                        }
            y.30.R4.SR3.TR2.bootstrap.pruned <- tmp1 # Change here for each sample
            
#------------------------------------------------------------------
rep.seq.vec <- y.30.R5.SR3.TR1.pruned.longform # Change here for each sample
colnames(rep.seq.vec) <- "rep.seq"
tmp1.list <- list()
for (i in 1:500)
{
  rep.seq.df <- as.data.frame(rep.seq.vec$rep.seq)
  tmp1 <- sample(rep.seq.df$`rep.seq.vec$rep.seq`, 9000, replace = T)
  tmp1.list[[i]] <- tmp1
}
      tmp1.df <- data.frame()
      tmp2.df <- matrix(nrow = 9000, ncol = 500)
      for (j in 1:9000)
      {
          for (i in 1:500)
          {
          tmp1.df <- as.data.frame(unlist(tmp1.list[[i]]))
          tmp2.df[j,i] <- as.character(tmp1.df[j,1])
          }
      }
            length.unique.list <- list()
            tab.1 <- data.frame()
            freq.tmp <- data.frame()
            tmp2.tab <- list()
            for (i in 1:500)
            {
              tab.1 <- as.data.frame(table(tmp2.df[,i]))
              freq.tmp <- tab.1$Freq
              length.unique.list[i] <- length(tab.1[,1])
              tmp2.tab[[i]] <- freq.tmp 
            }
            collength = 5 
            cutoff.val = 50
            tmp1 <- matrix(ncol = collength, nrow = 500) 
                        for (i in 1:500)
                        {
                          tmp1[i,1] <- length(which(tmp2.tab[[i]] > cutoff.val)) #HDP initial
                          tmp1[i,2] <- length(which(tmp2.tab[[i]] < cutoff.val & tmp2.tab[[i]] > 0)) #LDP initial
                          tmp1[i,3] <- sum(tmp2.tab[[i]][tmp2.tab[[i]]>cutoff.val]) #HDP final
                          tmp1[i,4] <- sum(tmp2.tab[[i]][tmp2.tab[[i]]<cutoff.val]) #LDP final
                          tmp1[i,5] <- as.numeric(unlist(length.unique.list[[i]]))
                        }
            y.30.R5.SR3.TR1.bootstrap.pruned <- tmp1 # Change here for each sample
            
#------------------------------------------------------------------
rep.seq.vec <- y.30.R5.SR3.TR2.pruned.longform # Change here for each sample
colnames(rep.seq.vec) <- "rep.seq"
tmp1.list <- list()
for (i in 1:500)
{
  rep.seq.df <- as.data.frame(rep.seq.vec$rep.seq)
  tmp1 <- sample(rep.seq.df$`rep.seq.vec$rep.seq`, 9000, replace = T)
  tmp1.list[[i]] <- tmp1
}
      tmp1.df <- data.frame()
      tmp2.df <- matrix(nrow = 9000, ncol = 500)
      for (j in 1:9000)
      {
          for (i in 1:500)
          {
          tmp1.df <- as.data.frame(unlist(tmp1.list[[i]]))
          tmp2.df[j,i] <- as.character(tmp1.df[j,1])
          }
      }
            length.unique.list <- list()
            tab.1 <- data.frame()
            freq.tmp <- data.frame()
            tmp2.tab <- list()
            for (i in 1:500)
            {
              tab.1 <- as.data.frame(table(tmp2.df[,i]))
              freq.tmp <- tab.1$Freq
              length.unique.list[i] <- length(tab.1[,1])
              tmp2.tab[[i]] <- freq.tmp 
            }
            collength = 5 
            cutoff.val = 50
            tmp1 <- matrix(ncol = collength, nrow = 500) 
                        for (i in 1:500)
                        {
                          tmp1[i,1] <- length(which(tmp2.tab[[i]] > cutoff.val)) #HDP initial
                          tmp1[i,2] <- length(which(tmp2.tab[[i]] < cutoff.val & tmp2.tab[[i]] > 0)) #LDP initial
                          tmp1[i,3] <- sum(tmp2.tab[[i]][tmp2.tab[[i]]>cutoff.val]) #HDP final
                          tmp1[i,4] <- sum(tmp2.tab[[i]][tmp2.tab[[i]]<cutoff.val]) #LDP final
                          tmp1[i,5] <- as.numeric(unlist(length.unique.list[[i]]))
                        }
           y.30.R5.SR3.TR2.bootstrap.pruned <- tmp1 # Change here for each sample

#------------------------------------------------------------------
rep.seq.vec <- y.30.R6.SR3.TR1.pruned.longform # Change here for each sample
colnames(rep.seq.vec) <- "rep.seq"
tmp1.list <- list()
for (i in 1:500)
{
  rep.seq.df <- as.data.frame(rep.seq.vec$rep.seq)
  tmp1 <- sample(rep.seq.df$`rep.seq.vec$rep.seq`, 9000, replace = T)
  tmp1.list[[i]] <- tmp1
}
      tmp1.df <- data.frame()
      tmp2.df <- matrix(nrow = 9000, ncol = 500)
      for (j in 1:9000)
      {
          for (i in 1:500)
          {
          tmp1.df <- as.data.frame(unlist(tmp1.list[[i]]))
          tmp2.df[j,i] <- as.character(tmp1.df[j,1])
          }
      }
            length.unique.list <- list()
            tab.1 <- data.frame()
            freq.tmp <- data.frame()
            tmp2.tab <- list()
            for (i in 1:500)
            {
              tab.1 <- as.data.frame(table(tmp2.df[,i]))
              freq.tmp <- tab.1$Freq
              length.unique.list[i] <- length(tab.1[,1])
              tmp2.tab[[i]] <- freq.tmp 
            }
            collength = 5 
            cutoff.val = 50
            tmp1 <- matrix(ncol = collength, nrow = 500) 
                        for (i in 1:500)
                        {
                          tmp1[i,1] <- length(which(tmp2.tab[[i]] > cutoff.val)) #HDP initial
                          tmp1[i,2] <- length(which(tmp2.tab[[i]] < cutoff.val & tmp2.tab[[i]] > 0)) #LDP initial
                          tmp1[i,3] <- sum(tmp2.tab[[i]][tmp2.tab[[i]]>cutoff.val]) #HDP final
                          tmp1[i,4] <- sum(tmp2.tab[[i]][tmp2.tab[[i]]<cutoff.val]) #LDP final
                          tmp1[i,5] <- as.numeric(unlist(length.unique.list[[i]]))
                        }
           y.30.R6.SR3.TR1.bootstrap.pruned <- tmp1 # Change here for each sample
#------------------------------------------------------------------
rep.seq.vec <- y.30.R6.SR3.TR2.pruned.longform # Change here for each sample
colnames(rep.seq.vec) <- "rep.seq"
tmp1.list <- list()
for (i in 1:500)
{
  rep.seq.df <- as.data.frame(rep.seq.vec$rep.seq)
  tmp1 <- sample(rep.seq.df$`rep.seq.vec$rep.seq`, 9000, replace = T)
  tmp1.list[[i]] <- tmp1
}
      tmp1.df <- data.frame()
      tmp2.df <- matrix(nrow = 9000, ncol = 500)
      for (j in 1:9000)
      {
          for (i in 1:500)
          {
          tmp1.df <- as.data.frame(unlist(tmp1.list[[i]]))
          tmp2.df[j,i] <- as.character(tmp1.df[j,1])
          }
      }
            length.unique.list <- list()
            tab.1 <- data.frame()
            freq.tmp <- data.frame()
            tmp2.tab <- list()
            for (i in 1:500)
            {
              tab.1 <- as.data.frame(table(tmp2.df[,i]))
              freq.tmp <- tab.1$Freq
              length.unique.list[i] <- length(tab.1[,1])
              tmp2.tab[[i]] <- freq.tmp 
            }
            collength = 5 
            cutoff.val = 50
            tmp1 <- matrix(ncol = collength, nrow = 500) 
                        for (i in 1:500)
                        {
                          tmp1[i,1] <- length(which(tmp2.tab[[i]] > cutoff.val)) #HDP initial
                          tmp1[i,2] <- length(which(tmp2.tab[[i]] < cutoff.val & tmp2.tab[[i]] > 0)) #LDP initial
                          tmp1[i,3] <- sum(tmp2.tab[[i]][tmp2.tab[[i]]>cutoff.val]) #HDP final
                          tmp1[i,4] <- sum(tmp2.tab[[i]][tmp2.tab[[i]]<cutoff.val]) #LDP final
                          tmp1[i,5] <- as.numeric(unlist(length.unique.list[[i]]))
                        }
           y.30.R6.SR3.TR2.bootstrap.pruned <- tmp1 # Change here for each sample

#------------------------------------------------------------------
rep.seq.vec <- y.30.R7.SR3.TR1.pruned.longform # Change here for each sample
colnames(rep.seq.vec) <- "rep.seq"
tmp1.list <- list()
for (i in 1:500)
{
  rep.seq.df <- as.data.frame(rep.seq.vec$rep.seq)
  tmp1 <- sample(rep.seq.df$`rep.seq.vec$rep.seq`, 9000, replace = T)
  tmp1.list[[i]] <- tmp1
}
      tmp1.df <- data.frame()
      tmp2.df <- matrix(nrow = 9000, ncol = 500)
      for (j in 1:9000)
      {
          for (i in 1:500)
          {
          tmp1.df <- as.data.frame(unlist(tmp1.list[[i]]))
          tmp2.df[j,i] <- as.character(tmp1.df[j,1])
          }
      }
            length.unique.list <- list()
            tab.1 <- data.frame()
            freq.tmp <- data.frame()
            tmp2.tab <- list()
            for (i in 1:500)
            {
              tab.1 <- as.data.frame(table(tmp2.df[,i]))
              freq.tmp <- tab.1$Freq
              length.unique.list[i] <- length(tab.1[,1])
              tmp2.tab[[i]] <- freq.tmp 
            }
            collength = 5 
            cutoff.val = 50
            tmp1 <- matrix(ncol = collength, nrow = 500) 
                        for (i in 1:500)
                        {
                          tmp1[i,1] <- length(which(tmp2.tab[[i]] > cutoff.val)) #HDP initial
                          tmp1[i,2] <- length(which(tmp2.tab[[i]] < cutoff.val & tmp2.tab[[i]] > 0)) #LDP initial
                          tmp1[i,3] <- sum(tmp2.tab[[i]][tmp2.tab[[i]]>cutoff.val]) #HDP final
                          tmp1[i,4] <- sum(tmp2.tab[[i]][tmp2.tab[[i]]<cutoff.val]) #LDP final
                          tmp1[i,5] <- as.numeric(unlist(length.unique.list[[i]]))
                        }
           y.30.R7.SR3.TR1.bootstrap.pruned <- tmp1 # Change here for each sample

#------------------------------------------------------------------
rep.seq.vec <- y.30.R7.SR3.TR2.pruned.longform # Change here for each sample
colnames(rep.seq.vec) <- "rep.seq"
tmp1.list <- list()
for (i in 1:500)
{
  rep.seq.df <- as.data.frame(rep.seq.vec$rep.seq)
  tmp1 <- sample(rep.seq.df$`rep.seq.vec$rep.seq`, 9000, replace = T)
  tmp1.list[[i]] <- tmp1
}
      tmp1.df <- data.frame()
      tmp2.df <- matrix(nrow = 9000, ncol = 500)
      for (j in 1:9000)
      {
          for (i in 1:500)
          {
          tmp1.df <- as.data.frame(unlist(tmp1.list[[i]]))
          tmp2.df[j,i] <- as.character(tmp1.df[j,1])
          }
      }
            length.unique.list <- list()
            tab.1 <- data.frame()
            freq.tmp <- data.frame()
            tmp2.tab <- list()
            for (i in 1:500)
            {
              tab.1 <- as.data.frame(table(tmp2.df[,i]))
              freq.tmp <- tab.1$Freq
              length.unique.list[i] <- length(tab.1[,1])
              tmp2.tab[[i]] <- freq.tmp 
            }
            collength = 5 
            cutoff.val = 50
            tmp1 <- matrix(ncol = collength, nrow = 500) 
                        for (i in 1:500)
                        {
                          tmp1[i,1] <- length(which(tmp2.tab[[i]] > cutoff.val)) #HDP initial
                          tmp1[i,2] <- length(which(tmp2.tab[[i]] < cutoff.val & tmp2.tab[[i]] > 0)) #LDP initial
                          tmp1[i,3] <- sum(tmp2.tab[[i]][tmp2.tab[[i]]>cutoff.val]) #HDP final
                          tmp1[i,4] <- sum(tmp2.tab[[i]][tmp2.tab[[i]]<cutoff.val]) #LDP final
                          tmp1[i,5] <- as.numeric(unlist(length.unique.list[[i]]))
                        }
           y.30.R7.SR3.TR2.bootstrap.pruned <- tmp1 # Change here for each sample
           
#------------------------------------------------------------------
rep.seq.vec <- a.30.R1.SR1.pruned.longform # Change here for each sample
colnames(rep.seq.vec) <- "rep.seq"
tmp1.list <- list()
for (i in 1:500)
{
  rep.seq.df <- as.data.frame(rep.seq.vec$rep.seq)
  tmp1 <- sample(rep.seq.df$`rep.seq.vec$rep.seq`, 2400, replace = T)
  tmp1.list[[i]] <- tmp1
}
      tmp1.df <- data.frame()
      tmp2.df <- matrix(nrow = 2400, ncol = 500)
      for (j in 1:2400)
      {
          for (i in 1:500)
          {
          tmp1.df <- as.data.frame(unlist(tmp1.list[[i]]))
          tmp2.df[j,i] <- as.character(tmp1.df[j,1])
          }
      }
            length.unique.list <- list()
            tab.1 <- data.frame()
            freq.tmp <- data.frame()
            tmp2.tab <- list()
            for (i in 1:500)
            {
              tab.1 <- as.data.frame(table(tmp2.df[,i]))
              freq.tmp <- tab.1$Freq
              length.unique.list[i] <- length(tab.1[,1])
              tmp2.tab[[i]] <- freq.tmp 
            }
            collength = 5 
            cutoff.val = 50
            tmp1 <- matrix(ncol = collength, nrow = 500) 
                        for (i in 1:500)
                        {
                          tmp1[i,1] <- length(which(tmp2.tab[[i]] > cutoff.val)) #HDP initial
                          tmp1[i,2] <- length(which(tmp2.tab[[i]] < cutoff.val & tmp2.tab[[i]] > 0)) #LDP initial
                          tmp1[i,3] <- sum(tmp2.tab[[i]][tmp2.tab[[i]]>cutoff.val]) #HDP final
                          tmp1[i,4] <- sum(tmp2.tab[[i]][tmp2.tab[[i]]<cutoff.val]) #LDP final
                          tmp1[i,5] <- as.numeric(unlist(length.unique.list[[i]]))
                        }
           a.30.R1.SR1.bootstrap.pruned <- tmp1 # Change here for each sample
           
#------------------------------------------------------------------
rep.seq.vec <- a.30.R2.SR1.pruned.longform # Change here for each sample
colnames(rep.seq.vec) <- "rep.seq"
tmp1.list <- list()
for (i in 1:500)
{
  rep.seq.df <- as.data.frame(rep.seq.vec$rep.seq)
  tmp1 <- sample(rep.seq.df$`rep.seq.vec$rep.seq`, 2400, replace = T)
  tmp1.list[[i]] <- tmp1
}
      tmp1.df <- data.frame()
      tmp2.df <- matrix(nrow = 2400, ncol = 500)
      for (j in 1:2400)
      {
          for (i in 1:500)
          {
          tmp1.df <- as.data.frame(unlist(tmp1.list[[i]]))
          tmp2.df[j,i] <- as.character(tmp1.df[j,1])
          }
      }
            length.unique.list <- list()
            tab.1 <- data.frame()
            freq.tmp <- data.frame()
            tmp2.tab <- list()
            for (i in 1:500)
            {
              tab.1 <- as.data.frame(table(tmp2.df[,i]))
              freq.tmp <- tab.1$Freq
              length.unique.list[i] <- length(tab.1[,1])
              tmp2.tab[[i]] <- freq.tmp 
            }
            collength = 5 
            cutoff.val = 50
            tmp1 <- matrix(ncol = collength, nrow = 500) 
                        for (i in 1:500)
                        {
                          tmp1[i,1] <- length(which(tmp2.tab[[i]] > cutoff.val)) #HDP initial
                          tmp1[i,2] <- length(which(tmp2.tab[[i]] < cutoff.val & tmp2.tab[[i]] > 0)) #LDP initial
                          tmp1[i,3] <- sum(tmp2.tab[[i]][tmp2.tab[[i]]>cutoff.val]) #HDP final
                          tmp1[i,4] <- sum(tmp2.tab[[i]][tmp2.tab[[i]]<cutoff.val]) #LDP final
                          tmp1[i,5] <- as.numeric(unlist(length.unique.list[[i]]))
                        }
           a.30.R2.SR1.bootstrap.pruned <- tmp1 # Change here for each sample
           
#------------------------------------------------------------------
rep.seq.vec <- a.30.R3.SR1.pruned.longform # Change here for each sample
colnames(rep.seq.vec) <- "rep.seq"
tmp1.list <- list()
for (i in 1:500)
{
  rep.seq.df <- as.data.frame(rep.seq.vec$rep.seq)
  tmp1 <- sample(rep.seq.df$`rep.seq.vec$rep.seq`, 2400, replace = T)
  tmp1.list[[i]] <- tmp1
}
      tmp1.df <- data.frame()
      tmp2.df <- matrix(nrow = 2400, ncol = 500)
      for (j in 1:2400)
      {
          for (i in 1:500)
          {
          tmp1.df <- as.data.frame(unlist(tmp1.list[[i]]))
          tmp2.df[j,i] <- as.character(tmp1.df[j,1])
          }
      }
            length.unique.list <- list()
            tab.1 <- data.frame()
            freq.tmp <- data.frame()
            tmp2.tab <- list()
            for (i in 1:500)
            {
              tab.1 <- as.data.frame(table(tmp2.df[,i]))
              freq.tmp <- tab.1$Freq
              length.unique.list[i] <- length(tab.1[,1])
              tmp2.tab[[i]] <- freq.tmp 
            }
            collength = 5 
            cutoff.val = 50
            tmp1 <- matrix(ncol = collength, nrow = 500) 
                        for (i in 1:500)
                        {
                          tmp1[i,1] <- length(which(tmp2.tab[[i]] > cutoff.val)) #HDP initial
                          tmp1[i,2] <- length(which(tmp2.tab[[i]] < cutoff.val & tmp2.tab[[i]] > 0)) #LDP initial
                          tmp1[i,3] <- sum(tmp2.tab[[i]][tmp2.tab[[i]]>cutoff.val]) #HDP final
                          tmp1[i,4] <- sum(tmp2.tab[[i]][tmp2.tab[[i]]<cutoff.val]) #LDP final
                          tmp1[i,5] <- as.numeric(unlist(length.unique.list[[i]]))
                        }
           a.30.R3.SR1.bootstrap.pruned <- tmp1 # Change here for each sample
           
#------------------------------------------------------------------
rep.seq.vec <- a.30.R4.SR2.pruned.longform # Change here for each sample
colnames(rep.seq.vec) <- "rep.seq"
tmp1.list <- list()
for (i in 1:500)
{
  rep.seq.df <- as.data.frame(rep.seq.vec$rep.seq)
  tmp1 <- sample(rep.seq.df$`rep.seq.vec$rep.seq`, 55000, replace = T)
  tmp1.list[[i]] <- tmp1
}
      tmp1.df <- data.frame()
      tmp2.df <- matrix(nrow = 55000, ncol = 500)
      for (j in 1:55000)
      {
          for (i in 1:500)
          {
          tmp1.df <- as.data.frame(unlist(tmp1.list[[i]]))
          tmp2.df[j,i] <- as.character(tmp1.df[j,1])
          }
      }
            length.unique.list <- list()
            tab.1 <- data.frame()
            freq.tmp <- data.frame()
            tmp2.tab <- list()
            for (i in 1:500)
            {
              tab.1 <- as.data.frame(table(tmp2.df[,i]))
              freq.tmp <- tab.1$Freq
              length.unique.list[i] <- length(tab.1[,1])
              tmp2.tab[[i]] <- freq.tmp 
            }
            collength = 5 
            cutoff.val = 50
            tmp1 <- matrix(ncol = collength, nrow = 500) 
                        for (i in 1:500)
                        {
                          tmp1[i,1] <- length(which(tmp2.tab[[i]] > cutoff.val)) #HDP initial
                          tmp1[i,2] <- length(which(tmp2.tab[[i]] < cutoff.val & tmp2.tab[[i]] > 0)) #LDP initial
                          tmp1[i,3] <- sum(tmp2.tab[[i]][tmp2.tab[[i]]>cutoff.val]) #HDP final
                          tmp1[i,4] <- sum(tmp2.tab[[i]][tmp2.tab[[i]]<cutoff.val]) #LDP final
                          tmp1[i,5] <- as.numeric(unlist(length.unique.list[[i]]))
                        }
           a.30.R4.SR2.bootstrap.pruned <- tmp1 # Change here for each sample
           
#------------------------------------------------------------------
rep.seq.vec <- a.30.R5.SR2.pruned.longform # Change here for each sample
colnames(rep.seq.vec) <- "rep.seq"
tmp1.list <- list()
for (i in 1:500)
{
  rep.seq.df <- as.data.frame(rep.seq.vec$rep.seq)
  tmp1 <- sample(rep.seq.df$`rep.seq.vec$rep.seq`, 55000, replace = T)
  tmp1.list[[i]] <- tmp1
}
      tmp1.df <- data.frame()
      tmp2.df <- matrix(nrow = 55000, ncol = 500)
      for (j in 1:55000)
      {
          for (i in 1:500)
          {
          tmp1.df <- as.data.frame(unlist(tmp1.list[[i]]))
          tmp2.df[j,i] <- as.character(tmp1.df[j,1])
          }
      }
            length.unique.list <- list()
            tab.1 <- data.frame()
            freq.tmp <- data.frame()
            tmp2.tab <- list()
            for (i in 1:500)
            {
              tab.1 <- as.data.frame(table(tmp2.df[,i]))
              freq.tmp <- tab.1$Freq
              length.unique.list[i] <- length(tab.1[,1])
              tmp2.tab[[i]] <- freq.tmp 
            }
            collength = 5 
            cutoff.val = 50
            tmp1 <- matrix(ncol = collength, nrow = 500) 
                        for (i in 1:500)
                        {
                          tmp1[i,1] <- length(which(tmp2.tab[[i]] > cutoff.val)) #HDP initial
                          tmp1[i,2] <- length(which(tmp2.tab[[i]] < cutoff.val & tmp2.tab[[i]] > 0)) #LDP initial
                          tmp1[i,3] <- sum(tmp2.tab[[i]][tmp2.tab[[i]]>cutoff.val]) #HDP final
                          tmp1[i,4] <- sum(tmp2.tab[[i]][tmp2.tab[[i]]<cutoff.val]) #LDP final
                          tmp1[i,5] <- as.numeric(unlist(length.unique.list[[i]]))
                        }
           a.30.R5.SR2.bootstrap.pruned <- tmp1 # Change here for each sample
           
#------------------------------------------------------------------
rep.seq.vec <- a.30.R6.SR2.pruned.longform # Change here for each sample
colnames(rep.seq.vec) <- "rep.seq"
tmp1.list <- list()
for (i in 1:500)
{
  rep.seq.df <- as.data.frame(rep.seq.vec$rep.seq)
  tmp1 <- sample(rep.seq.df$`rep.seq.vec$rep.seq`, 55000, replace = T)
  tmp1.list[[i]] <- tmp1
}
      tmp1.df <- data.frame()
      tmp2.df <- matrix(nrow = 55000, ncol = 500)
      for (j in 1:55000)
      {
          for (i in 1:500)
          {
          tmp1.df <- as.data.frame(unlist(tmp1.list[[i]]))
          tmp2.df[j,i] <- as.character(tmp1.df[j,1])
          }
      }
            length.unique.list <- list()
            tab.1 <- data.frame()
            freq.tmp <- data.frame()
            tmp2.tab <- list()
            for (i in 1:500)
            {
              tab.1 <- as.data.frame(table(tmp2.df[,i]))
              freq.tmp <- tab.1$Freq
              length.unique.list[i] <- length(tab.1[,1])
              tmp2.tab[[i]] <- freq.tmp 
            }
            collength = 5 
            cutoff.val = 50
            tmp1 <- matrix(ncol = collength, nrow = 500) 
                        for (i in 1:500)
                        {
                          tmp1[i,1] <- length(which(tmp2.tab[[i]] > cutoff.val)) #HDP initial
                          tmp1[i,2] <- length(which(tmp2.tab[[i]] < cutoff.val & tmp2.tab[[i]] > 0)) #LDP initial
                          tmp1[i,3] <- sum(tmp2.tab[[i]][tmp2.tab[[i]]>cutoff.val]) #HDP final
                          tmp1[i,4] <- sum(tmp2.tab[[i]][tmp2.tab[[i]]<cutoff.val]) #LDP final
                          tmp1[i,5] <- as.numeric(unlist(length.unique.list[[i]]))
                        }
           a.30.R6.SR2.bootstrap.pruned <- tmp1 # Change here for each sample
           
#------------------------------------------------------------------
rep.seq.vec <- a.30.R7.SR2.pruned.longform # Change here for each sample
colnames(rep.seq.vec) <- "rep.seq"
tmp1.list <- list()
for (i in 1:500)
{
  rep.seq.df <- as.data.frame(rep.seq.vec$rep.seq)
  tmp1 <- sample(rep.seq.df$`rep.seq.vec$rep.seq`, 55000, replace = T)
  tmp1.list[[i]] <- tmp1
}
      tmp1.df <- data.frame()
      tmp2.df <- matrix(nrow = 55000, ncol = 500)
      for (j in 1:55000)
      {
          for (i in 1:500)
          {
          tmp1.df <- as.data.frame(unlist(tmp1.list[[i]]))
          tmp2.df[j,i] <- as.character(tmp1.df[j,1])
          }
      }
            length.unique.list <- list()
            tab.1 <- data.frame()
            freq.tmp <- data.frame()
            tmp2.tab <- list()
            for (i in 1:500)
            {
              tab.1 <- as.data.frame(table(tmp2.df[,i]))
              freq.tmp <- tab.1$Freq
              length.unique.list[i] <- length(tab.1[,1])
              tmp2.tab[[i]] <- freq.tmp 
            }
            collength = 5 
            cutoff.val = 50
            tmp1 <- matrix(ncol = collength, nrow = 500) 
                        for (i in 1:500)
                        {
                          tmp1[i,1] <- length(which(tmp2.tab[[i]] > cutoff.val)) #HDP initial
                          tmp1[i,2] <- length(which(tmp2.tab[[i]] < cutoff.val & tmp2.tab[[i]] > 0)) #LDP initial
                          tmp1[i,3] <- sum(tmp2.tab[[i]][tmp2.tab[[i]]>cutoff.val]) #HDP final
                          tmp1[i,4] <- sum(tmp2.tab[[i]][tmp2.tab[[i]]<cutoff.val]) #LDP final
                          tmp1[i,5] <- as.numeric(unlist(length.unique.list[[i]]))
                        }
           a.30.R7.SR2.bootstrap.pruned <- tmp1 # Change here for each sample
           
#------------------------------------------------------------------
rep.seq.vec <- a.30.R8.SR2.pruned.longform # Change here for each sample
colnames(rep.seq.vec) <- "rep.seq"
tmp1.list <- list()
for (i in 1:500)
{
  rep.seq.df <- as.data.frame(rep.seq.vec$rep.seq)
  tmp1 <- sample(rep.seq.df$`rep.seq.vec$rep.seq`, 55000, replace = T)
  tmp1.list[[i]] <- tmp1
}
      tmp1.df <- data.frame()
      tmp2.df <- matrix(nrow = 55000, ncol = 500)
      for (j in 1:55000)
      {
          for (i in 1:500)
          {
          tmp1.df <- as.data.frame(unlist(tmp1.list[[i]]))
          tmp2.df[j,i] <- as.character(tmp1.df[j,1])
          }
      }
            length.unique.list <- list()
            tab.1 <- data.frame()
            freq.tmp <- data.frame()
            tmp2.tab <- list()
            for (i in 1:500)
            {
              tab.1 <- as.data.frame(table(tmp2.df[,i]))
              freq.tmp <- tab.1$Freq
              length.unique.list[i] <- length(tab.1[,1])
              tmp2.tab[[i]] <- freq.tmp 
            }
            collength = 5 
            cutoff.val = 50
            tmp1 <- matrix(ncol = collength, nrow = 500) 
                        for (i in 1:500)
                        {
                          tmp1[i,1] <- length(which(tmp2.tab[[i]] > cutoff.val)) #HDP initial
                          tmp1[i,2] <- length(which(tmp2.tab[[i]] < cutoff.val & tmp2.tab[[i]] > 0)) #LDP initial
                          tmp1[i,3] <- sum(tmp2.tab[[i]][tmp2.tab[[i]]>cutoff.val]) #HDP final
                          tmp1[i,4] <- sum(tmp2.tab[[i]][tmp2.tab[[i]]<cutoff.val]) #LDP final
                          tmp1[i,5] <- as.numeric(unlist(length.unique.list[[i]]))
                        }
           a.30.R8.SR2.bootstrap.pruned <- tmp1 # Change here for each sample
           
#------------------------------------------------------------------
rep.seq.vec <- a.30.R9.SR3.TR1.pruned.longform # Change here for each sample
colnames(rep.seq.vec) <- "rep.seq"
tmp1.list <- list()
for (i in 1:500)
{
  rep.seq.df <- as.data.frame(rep.seq.vec$rep.seq)
  tmp1 <- sample(rep.seq.df$`rep.seq.vec$rep.seq`, 9000, replace = T)
  tmp1.list[[i]] <- tmp1
}
      tmp1.df <- data.frame()
      tmp2.df <- matrix(nrow = 9000, ncol = 500)
      for (j in 1:9000)
      {
          for (i in 1:500)
          {
          tmp1.df <- as.data.frame(unlist(tmp1.list[[i]]))
          tmp2.df[j,i] <- as.character(tmp1.df[j,1])
          }
      }
            length.unique.list <- list()
            tab.1 <- data.frame()
            freq.tmp <- data.frame()
            tmp2.tab <- list()
            for (i in 1:500)
            {
              tab.1 <- as.data.frame(table(tmp2.df[,i]))
              freq.tmp <- tab.1$Freq
              length.unique.list[i] <- length(tab.1[,1])
              tmp2.tab[[i]] <- freq.tmp 
            }
            collength = 5 
            cutoff.val = 50
            tmp1 <- matrix(ncol = collength, nrow = 500) 
                        for (i in 1:500)
                        {
                          tmp1[i,1] <- length(which(tmp2.tab[[i]] > cutoff.val)) #HDP initial
                          tmp1[i,2] <- length(which(tmp2.tab[[i]] < cutoff.val & tmp2.tab[[i]] > 0)) #LDP initial
                          tmp1[i,3] <- sum(tmp2.tab[[i]][tmp2.tab[[i]]>cutoff.val]) #HDP final
                          tmp1[i,4] <- sum(tmp2.tab[[i]][tmp2.tab[[i]]<cutoff.val]) #LDP final
                          tmp1[i,5] <- as.numeric(unlist(length.unique.list[[i]]))
                        }
           a.30.R9.SR3.TR1.bootstrap.pruned <- tmp1 # Change here for each sample
           
#------------------------------------------------------------------
rep.seq.vec <- a.30.R9.SR3.TR2.pruned.longform # Change here for each sample
colnames(rep.seq.vec) <- "rep.seq"
tmp1.list <- list()
for (i in 1:500)
{
  rep.seq.df <- as.data.frame(rep.seq.vec$rep.seq)
  tmp1 <- sample(rep.seq.df$`rep.seq.vec$rep.seq`, 9000, replace = T)
  tmp1.list[[i]] <- tmp1
}
      tmp1.df <- data.frame()
      tmp2.df <- matrix(nrow = 9000, ncol = 500)
      for (j in 1:9000)
      {
          for (i in 1:500)
          {
          tmp1.df <- as.data.frame(unlist(tmp1.list[[i]]))
          tmp2.df[j,i] <- as.character(tmp1.df[j,1])
          }
      }
            length.unique.list <- list()
            tab.1 <- data.frame()
            freq.tmp <- data.frame()
            tmp2.tab <- list()
            for (i in 1:500)
            {
              tab.1 <- as.data.frame(table(tmp2.df[,i]))
              freq.tmp <- tab.1$Freq
              length.unique.list[i] <- length(tab.1[,1])
              tmp2.tab[[i]] <- freq.tmp 
            }
            collength = 5 
            cutoff.val = 50
            tmp1 <- matrix(ncol = collength, nrow = 500) 
                        for (i in 1:500)
                        {
                          tmp1[i,1] <- length(which(tmp2.tab[[i]] > cutoff.val)) #HDP initial
                          tmp1[i,2] <- length(which(tmp2.tab[[i]] < cutoff.val & tmp2.tab[[i]] > 0)) #LDP initial
                          tmp1[i,3] <- sum(tmp2.tab[[i]][tmp2.tab[[i]]>cutoff.val]) #HDP final
                          tmp1[i,4] <- sum(tmp2.tab[[i]][tmp2.tab[[i]]<cutoff.val]) #LDP final
                          tmp1[i,5] <- as.numeric(unlist(length.unique.list[[i]]))
                        }
           a.30.R9.SR3.TR2.bootstrap.pruned <- tmp1 # Change here for each sample
           
#------------------------------------------------------------------
rep.seq.vec <- a.30.R10.SR3.TR1.pruned.longform # Change here for each sample
colnames(rep.seq.vec) <- "rep.seq"
tmp1.list <- list()
for (i in 1:500)
{
  rep.seq.df <- as.data.frame(rep.seq.vec$rep.seq)
  tmp1 <- sample(rep.seq.df$`rep.seq.vec$rep.seq`, 9000, replace = T)
  tmp1.list[[i]] <- tmp1
}
      tmp1.df <- data.frame()
      tmp2.df <- matrix(nrow = 9000, ncol = 500)
      for (j in 1:9000)
      {
          for (i in 1:500)
          {
          tmp1.df <- as.data.frame(unlist(tmp1.list[[i]]))
          tmp2.df[j,i] <- as.character(tmp1.df[j,1])
          }
      }
            length.unique.list <- list()
            tab.1 <- data.frame()
            freq.tmp <- data.frame()
            tmp2.tab <- list()
            for (i in 1:500)
            {
              tab.1 <- as.data.frame(table(tmp2.df[,i]))
              freq.tmp <- tab.1$Freq
              length.unique.list[i] <- length(tab.1[,1])
              tmp2.tab[[i]] <- freq.tmp 
            }
            collength = 5 
            cutoff.val = 50
            tmp1 <- matrix(ncol = collength, nrow = 500) 
                        for (i in 1:500)
                        {
                          tmp1[i,1] <- length(which(tmp2.tab[[i]] > cutoff.val)) #HDP initial
                          tmp1[i,2] <- length(which(tmp2.tab[[i]] < cutoff.val & tmp2.tab[[i]] > 0)) #LDP initial
                          tmp1[i,3] <- sum(tmp2.tab[[i]][tmp2.tab[[i]]>cutoff.val]) #HDP final
                          tmp1[i,4] <- sum(tmp2.tab[[i]][tmp2.tab[[i]]<cutoff.val]) #LDP final
                          tmp1[i,5] <- as.numeric(unlist(length.unique.list[[i]]))
                        }
           a.30.R10.SR3.TR1.bootstrap.pruned <- tmp1 # Change here for each sample
           
#------------------------------------------------------------------
rep.seq.vec <- a.30.R10.SR3.TR2.pruned.longform # Change here for each sample
colnames(rep.seq.vec) <- "rep.seq"
tmp1.list <- list()
for (i in 1:500)
{
  rep.seq.df <- as.data.frame(rep.seq.vec$rep.seq)
  tmp1 <- sample(rep.seq.df$`rep.seq.vec$rep.seq`, 9000, replace = T)
  tmp1.list[[i]] <- tmp1
}
      tmp1.df <- data.frame()
      tmp2.df <- matrix(nrow = 9000, ncol = 500)
      for (j in 1:9000)
      {
          for (i in 1:500)
          {
          tmp1.df <- as.data.frame(unlist(tmp1.list[[i]]))
          tmp2.df[j,i] <- as.character(tmp1.df[j,1])
          }
      }
            length.unique.list <- list()
            tab.1 <- data.frame()
            freq.tmp <- data.frame()
            tmp2.tab <- list()
            for (i in 1:500)
            {
              tab.1 <- as.data.frame(table(tmp2.df[,i]))
              freq.tmp <- tab.1$Freq
              length.unique.list[i] <- length(tab.1[,1])
              tmp2.tab[[i]] <- freq.tmp 
            }
            collength = 5 
            cutoff.val = 50
            tmp1 <- matrix(ncol = collength, nrow = 500) 
                        for (i in 1:500)
                        {
                          tmp1[i,1] <- length(which(tmp2.tab[[i]] > cutoff.val)) #HDP initial
                          tmp1[i,2] <- length(which(tmp2.tab[[i]] < cutoff.val & tmp2.tab[[i]] > 0)) #LDP initial
                          tmp1[i,3] <- sum(tmp2.tab[[i]][tmp2.tab[[i]]>cutoff.val]) #HDP final
                          tmp1[i,4] <- sum(tmp2.tab[[i]][tmp2.tab[[i]]<cutoff.val]) #LDP final
                          tmp1[i,5] <- as.numeric(unlist(length.unique.list[[i]]))
                        }
           a.30.R10.SR3.TR2.bootstrap.pruned <- tmp1 # Change here for each sample

colnames(DF1.R1.SR1.bootstrap.pruned) <- c("HDP.initial",'LDP.initial','HDP.final','LDP.final', 'total.unique')
colnames(DF1.R2.SR3.TR1.bootstrap.pruned) <- c("HDP.initial",'LDP.initial','HDP.final','LDP.final', 'total.unique')
colnames(DF1.R2.SR3.TR2.bootstrap.pruned) <- c("HDP.initial",'LDP.initial','HDP.final','LDP.final', 'total.unique')
colnames(y.90.R1.SR1.bootstrap.pruned) <- c("HDP.initial",'LDP.initial','HDP.final','LDP.final', 'total.unique')
colnames(y.90.R2.SR3.TR1.bootstrap.pruned) <- c("HDP.initial",'LDP.initial','HDP.final','LDP.final', 'total.unique')
colnames(y.90.R2.SR3.TR2.bootstrap.pruned) <- c("HDP.initial",'LDP.initial','HDP.final','LDP.final', 'total.unique')
colnames(y.90.R3.SR3.TR1.bootstrap.pruned) <- c("HDP.initial",'LDP.initial','HDP.final','LDP.final', 'total.unique')
colnames(y.90.R3.SR3.TR2.bootstrap.pruned) <- c("HDP.initial",'LDP.initial','HDP.final','LDP.final', 'total.unique')
colnames(y.90.R4.SR3.TR1.bootstrap.pruned) <- c("HDP.initial",'LDP.initial','HDP.final','LDP.final', 'total.unique')
colnames(y.90.R4.SR3.TR2.bootstrap.pruned) <- c("HDP.initial",'LDP.initial','HDP.final','LDP.final', 'total.unique')
colnames(y.90.R5.SR3.TR1.bootstrap.pruned) <- c("HDP.initial",'LDP.initial','HDP.final','LDP.final', 'total.unique')
colnames(y.90.R5.SR3.TR2.bootstrap.pruned) <- c("HDP.initial",'LDP.initial','HDP.final','LDP.final', 'total.unique')
colnames(y.30.R1.SR1.bootstrap.pruned) <- c("HDP.initial",'LDP.initial','HDP.final','LDP.final', 'total.unique')
colnames(y.30.R2.SR2.bootstrap.pruned) <- c("HDP.initial",'LDP.initial','HDP.final','LDP.final', 'total.unique')
colnames(y.30.R3.SR2.bootstrap.pruned) <- c("HDP.initial",'LDP.initial','HDP.final','LDP.final', 'total.unique')
colnames(y.30.R4.SR3.TR1.bootstrap.pruned) <- c("HDP.initial",'LDP.initial','HDP.final','LDP.final', 'total.unique')
colnames(y.30.R4.SR3.TR2.bootstrap.pruned) <- c("HDP.initial",'LDP.initial','HDP.final','LDP.final', 'total.unique')
colnames(y.30.R5.SR3.TR1.bootstrap.pruned) <- c("HDP.initial",'LDP.initial','HDP.final','LDP.final', 'total.unique')
colnames(y.30.R5.SR3.TR2.bootstrap.pruned) <- c("HDP.initial",'LDP.initial','HDP.final','LDP.final', 'total.unique')
colnames(y.30.R6.SR3.TR1.bootstrap.pruned) <- c("HDP.initial",'LDP.initial','HDP.final','LDP.final', 'total.unique')
colnames(y.30.R6.SR3.TR2.bootstrap.pruned) <- c("HDP.initial",'LDP.initial','HDP.final','LDP.final', 'total.unique')
colnames(y.30.R7.SR3.TR1.bootstrap.pruned) <- c("HDP.initial",'LDP.initial','HDP.final','LDP.final', 'total.unique')
colnames(y.30.R7.SR3.TR2.bootstrap.pruned) <- c("HDP.initial",'LDP.initial','HDP.final','LDP.final', 'total.unique')
colnames(a.30.R1.SR1.bootstrap.pruned) <- c("HDP.initial",'LDP.initial','HDP.final','LDP.final', 'total.unique')
colnames(a.30.R2.SR1.bootstrap.pruned) <- c("HDP.initial",'LDP.initial','HDP.final','LDP.final', 'total.unique')
colnames(a.30.R3.SR1.bootstrap.pruned) <- c("HDP.initial",'LDP.initial','HDP.final','LDP.final', 'total.unique')
colnames(a.30.R4.SR2.bootstrap.pruned) <- c("HDP.initial",'LDP.initial','HDP.final','LDP.final', 'total.unique')
colnames(a.30.R5.SR2.bootstrap.pruned) <- c("HDP.initial",'LDP.initial','HDP.final','LDP.final', 'total.unique')
colnames(a.30.R6.SR2.bootstrap.pruned) <- c("HDP.initial",'LDP.initial','HDP.final','LDP.final', 'total.unique')
colnames(a.30.R7.SR2.bootstrap.pruned) <- c("HDP.initial",'LDP.initial','HDP.final','LDP.final', 'total.unique')
colnames(a.30.R8.SR2.bootstrap.pruned) <- c("HDP.initial",'LDP.initial','HDP.final','LDP.final', 'total.unique')
colnames(a.30.R9.SR3.TR1.bootstrap.pruned) <- c("HDP.initial",'LDP.initial','HDP.final','LDP.final', 'total.unique')
colnames(a.30.R9.SR3.TR2.bootstrap.pruned) <- c("HDP.initial",'LDP.initial','HDP.final','LDP.final', 'total.unique')
colnames(a.30.R10.SR3.TR1.bootstrap.pruned) <- c("HDP.initial",'LDP.initial','HDP.final','LDP.final', 'total.unique')
colnames(a.30.R10.SR3.TR2.bootstrap.pruned) <- c("HDP.initial",'LDP.initial','HDP.final','LDP.final', 'total.unique')
